|

### 2023-01-27 paper.Rmd
autogit

---
title: |
  <center>Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming</center>
  <center>Master Thesis - M.Sc. Business Education</center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Master Thesis</center>
  <center>FB 03: Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  pdf_document:
    # keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    includes:
      in_header: [header_files/settings.tex]
indent: false
fontsize: 11pt
bibliography: ./ref/ref.bib
link-citations: true
fig.width: 4in
fig.height: 3in
csl: csl/association-for-computing-machinery.csl
#csl: csl/harvard-cite-them-right.csl
#csl: csl/springer-science-reviews.csl
include-before: '`\thispagestyle{empty} \newpage{}`{=latex}'
---

@@

knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.pos = "!H")

@@

```{bash recompile_results, echo=TRUE, eval=FALSE, include=FALSE}

@@

The DAE-GP algorithm, first described by @dae-gp_2020_rtree, is summarized as a flowchart in \@ref(fig:dae-gp-flowchart). 
After setting the generation counter $g$ to $0$ and creating the initial population of solutions $P_0$, DAE-GP enters the main loop that checks if a termination criteria is satisfied (i.e. maximum number of generations or fitness evaluations is reached).
For each generation $g$ the fitness of all new individuals in $P_g$ is evaluated. During model building, DAE-GP selects a subset $X_g$ of the current population that is used as training data for the DAE-LSTM model $M_g$ which is trained to learn the properties of $X_g$. 
The trained model $M_g$ is then used for model sampling, partially mutated solutions from $P_G$ are propagated through $M_g$ to create a new population $P_{g+1}$. 
This process is repeated until the termination criteria is met and DAE-GP returns the highest fitness solutions.

```{r dae-gp-flowchart, echo=FALSE, fig.cap="Regular DAE-GP Flowchart", out.height="90%", out.width="50%"}
knitr::include_graphics("./img/flowcharts/dae-gp.png")
```

@@

```{r airfoil_dataset_description, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_vars.csv"),
  caption="Airfoil - Dataset Description"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

@@

```{r airfoil_function_set, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_function_set"),
  caption="Airfoil - Function Set"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

@@

```{r airfoil_fullRun_2hl_maxIndSize_params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_fullRun_2hl_maxIndSize_params"),
  caption="Airfoil - Parameter for full Run"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

@@

```{r full_run_realWorldSymReg_problems, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Overview - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
Table X summarizes the median best fitness achieved after running each algorithm for 10 runs using a population size of 500 individuals for 30 generations.^[P-Values are marked with asteriks (1,2,3) for ($\alpha$)-levels of $0.1$, $0.05$ and $0.01$]. The median best fitness over all 30 generations are visualized in figure X.

```{r full_run_realWorldSymReg_fitness, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

@@

```{r full_run_realWorldSymReg_best_solution_size, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

@@

```{r full_run_realWorldSymReg_popDiversity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

@@

```{r full_run_realWorldSymReg_epochsPerGen, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

>>>>

---
title: |
  <center>Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming</center>
  <center>Master Thesis - M.Sc. Business Education</center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Master Thesis</center>
  <center>FB 03: Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    includes:
      in_header: [header_files/settings.tex]
indent: false
fontsize: 11pt
bibliography: ./ref/ref.bib
link-citations: true
fig.width: 4in
fig.height: 3in
csl: csl/association-for-computing-machinery.csl
#csl: csl/harvard-cite-them-right.csl
#csl: csl/springer-science-reviews.csl
include-before: '`\thispagestyle{empty} \newpage{}`{=latex}'
---

@@

knitr::opts_chunk$set(
  echo = TRUE,
  fig.pos = "c",
  fig.align="center"
  )

@@

```{bash recompile-results, echo=TRUE, eval=FALSE, include=FALSE}

@@

The DAE-GP algorithm, first described by @dae-gp_2020_rtree, is summarized as a flowchart in \@ref(fig:daegp-flowchart).
After setting the generation counter $g$ to $0$ and creating the initial population of solutions $P_0$, DAE-GP enters the main loop that checks if a termination criteria is satisfied (i.e. maximum number of generations or fitness evaluations is reached).
For each generation $g$ the fitness of all new individuals in $P_g$ is evaluated. During model building, DAE-GP selects a subset $X_g$ of the current population that is used as training data for the DAE-LSTM model $M_g$ which is trained to learn the properties of $X_g$.
The trained model $M_g$ is then used for model sampling, partially mutated solutions from $P_G$ are propagated through $M_g$ to create a new population $P_{g+1}$.
This process is repeated until the termination criteria is met and DAE-GP returns the highest fitness solutions.

```{r daegp-flowchart, echo=FALSE, fig.cap="Regular DAE-GP Flowchart", out.height="90%", out.width="50%"}
knitr::include_graphics("./img/flowcharts/dae-gp.png")
```

@@

```{r airfoil-dataset-description, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_vars.csv"),
  caption="Airfoil - Dataset Description"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

@@

```{r airfoil-function-set, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_function_set"),
  caption="Airfoil - Function Set"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

@@

```{r airfoil-fullRun-2hl-maxIndSize-params, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/airfoil_fullRun_2hl_maxIndSize_params"),
  caption="Airfoil - Parameter for full Run"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

@@

```{r full-run-realWorldSymReg-problems, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Overview - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
Table X summarizes the median best fitness achieved after running each algorithm for 10 runs using a population size of 500 individuals for 30 generations.^[P-Values are marked with asteriks (1,2,3) for ($\alpha$)-levels of $0.1$, $0.05$ and $0.01$]. The median best fitness over all 30 generations are visualized in figure X.

```{r full-run-realWorldSymReg-fitness, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

@@

```{r full-run-realWorldSymReg-best-solution-size, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

@@

```{r full-run-realWorldSymReg-popDiversity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

@@

```{r full-run-realWorldSymReg-epochsPerGen, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)
